Cellct analysis

### 2019-11-05 code/cellcount.Rmd
started to add cellct plot just for samples we sequenced

>>>>

```{r}
cellct_in_seq <- short_names %>% 
  filter(have_seq==T)

cust_theme <- theme(legend.position = "none",
                    panel.grid.major.x = element_blank(), # remove vertical lines in background
                    panel.grid.minor.x = element_blank(),
                    axis.line=element_blank(), # remove x axis
                    axis.title.x=element_blank(), 
                    axis.text.x=element_blank(),
                    axis.ticks.x=element_blank(),
                    panel.spacing = unit(-0.01, "lines"), # remove space between facet panels
                    # strip.text.x = element_text(angle = 0, hjust=1.0, vjust = 0.8), # rotate facet labels 90
                    strip.background = element_blank()) # remove grey boxes around facet labs

cellct_order <- c("Cr","Sn","Cb","Ck","Cn","G","O")

cellct_in_seq_bar <- ggplot(cellct_in_seq, aes(x=alias %>% fct_reorder(elev_m), y=percent_of_sample)) +
  geom_bar(aes(fill=short_morpho_name), stat="identity") + # classic stacked relative abundance plot
  coord_flip() +
  facet_grid(~short_morpho_name, switch = "x") +
  labs( x="Sample ID", tag="B") +
  cust_theme

cellct_in_seq_bar
```
